% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}


\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{WSDM}{'2016 San Francisco, USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Question Answering using Structured and Semi-structured User Generated Content}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% 1st. author
\alignauthor
Denis Savenkov\\
       \affaddr{Emory University}\\
       \affaddr{Atlanta, USA}\\
       \email{denis.savenkov@emory.edu}
}

\maketitle
\begin{abstract}

The proposed thesis research is focusing on the effective utilization of different unstructured, semi-structured and structured data sources for factoid and non-factoid question answering.
Most of the existing factoid QA approaches incorporate text document collections and knowledge bases (KB).
However, these data sources are used rather independently for answer candidates generation, which are then merged and ranked together.
Text-based approaches find candidates solely in the retrieved text fragments, whereas knowledge base approaches only explore a neighborhood of identified question topic entities.
Such separation of data sources is limiting the ability of a QA system to find good candidates in the first place and rank them effectively using all the information available in the data sources.
In this thesis I propose to connect text documents and KB via entity linking and use this extended representation to improve both answer generation and ranking.
In non-factoid question answering one of the most effective strategies is retrieving answers to similar questions previously posted to community question answering (CQA) websites. Unfortunately, in many cases such questions are not available or challenging to find. Matching between a question and a regular passage from a text document is complicated because of the lexical gap and necessity for deep semantic understanding of answer utterances. In my thesis I propose to tackle these challenges with better web document structure understanding, which can be used to extract question-answer pairs from web forums, FAQ-pages and other documents. The proposed research directions will help to improve the performance of today's QA systems, and can guide future efforts on combining knowledge representations for AI tasks.


\end{abstract}

% A category with the (minimum) three required fields
%\category{H.3.3}{H.3.3 Information Search and Retrieval}{Retrieval models}
%\category{I.2.3}{Artificial Intelligence}{Answer/reason extraction}

%\keywords{Question Answering; Knowledge Bases; Web Search}

\section{Introduction}
\input{introduction.inc}

\section{Research Proposal}
\input{proposal.inc}

\section{Experiments}
\input{experiments.inc}

\section{Related Work}
\input{related_work.inc}

\vspace{-0.2cm}
\section{Discussion}
\vspace{-0.1cm}
\input{issues.inc}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\vspace{-0.2cm}
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\newpage

\appendix
%Appendix A
\section{Student statement}
I'm a 5th year PhD student at Emory University and during the course of my studies I've worked on a number of different topics, starting from click log analysis, study of mobile users behavior, search user assistance for difficult search tasks, information extraction and now question answering.
In addition I've spent 4 wonderful summers in Microsoft and Google working on search results diversity, entity linking, information extraction and coreference resolution.
From a wide range of topics I've worked on, I've decided to focus my thesis on question answering.
In several month I'm going to do a thesis proposal and WSDM Doctoral Consortium presents a great chance to discuss the proposed direction with experienced researchers with various background.
I hope to make a valuable contribution to the area and discussion with the experts will help me polish the plan for the future thesis.
The proposed topic involves several related areas, such as information retrieval, natural language processing, web search and mining, knowledge representation, knowledge base construction and semantic parsing.
Most of my work was in the information retrieval area, and I have less experience with knowledge representation and natural language processing.
Therefore, I would greatly appreciate a chance to attend the consortium and discuss the potential challenges and ways to improve the work with researches with complementary experiences, which can make my work more interesting for different communities.

\section{Advisor statement}
My name is Eugene Agichtein\footnote{http://www.mathcs.emory.edu/$\sim$eugene/}, and I am Denis Savenkov's Ph.D. advisor.
Denis is entering his 5th year as a PhD student at the Emory Mathematics \& Computer Science department. He is expected to present his thesis proposal in the next few months, and to defend his thesis within a year, likely by December 2016.
Denis has broad interests within Information Retrieval, and has done excellent work on a number of topics in IR.
In particular, he and his team placed in the top 3 teams at the Yandex Click prediction challenge, and subsequently won the "Search Engine Prediction" challenge, publishing a full SIGIR paper on the novel techniques they developed.
Denis has also done in-depth studies of community question answering data, resulting in a full ICWSM paper as well as interesting analysis of how (not) to support searchers during complex tasks.
The analysis of difficult, or failed, searches, led Denis to become interested in question answering, as a way of attacking some of the long standing challenges in search.
I believe Denis has the skills and the creativity to tackle the ambitious task he proposes, on combining information from unstructured text and knowledge bases for question answering.
Attending the doctoral consortium at WSDM will give Denis a chance to interact with leading experts in Web search, social media analysis and data mining, and especially those with complementary expertise to mine.
As an IR researcher, I am reasonably confident on advising Denis on the aspects of his thesis related to IR and QA over unstructured (text) data, but am less familiar with the work done in KD and linked data communities, both in academia or industry.
As Denis' thesis spans both areas, input from researchers who work on constructing and utilizing KBs, knowledge graphs and other structured sources is critical.
Participating in DC would be particularly beneficial to Denis this year, as he is at the stage of developing his thesis proposal.

\end{document}
